Algebraic Principles for Concurrency Verification Tools

### 2013-11-07 Paper/paper.tex
Started work on FINDP program

\begin{abstract}
  We investigate equational laws for the derivation of rely-guarantee
  style inference and refinement rules in the minimalistic setting of
  semirings. This algebraic level is linked with concrete programming
  models based on languages and execution traces. The approach has
  been implemented in Isabelle/HOL where the link between algebras and
  models supports reasoning about both the control and data flow of
  concurrent programs. This is illustrated by simple program
  verification examples.
\end{abstract}

>>>>

\begin{abstract}
  We investigate equational laws for the derivation of rely-guarantee
  style inference and refinement rules in the minimalistic setting of
  semirings. This algebraic level is linked with concrete programming
  models based on languages and execution traces. The approach has
  been implemented in Isabelle/HOL where the link between algebras and
  models supports reasoning about both the control and data flow of
  concurrent programs at varying levels of abstraction. Finally, we
  illustrate our approach via simple program verification examples.
\end{abstract}
